Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-09 paper.tex
abstract

    \begin{abstract}

>>>>

    \begin{abstract}
        The rate of data aquisition coupled with the volume of data obtained 
        from datasharing initiatives has lead to unprecedented amount of 
        neuroimaging data. This surge of open neuroimaging data is of great 
        importance to scientific advancement, however, it is currently 
        inaccessible to many research labs due to limited infrastructure and 
        lack of software available to faciliate processing. Despite the existance
        of many neuroimaging workflow engines, none of them are well adapted for
        the processing of neuroimaging Big Data. Generalized Big Data frameworks
        exist, however they may lack crucial aspects necessary to process neuroimaging
        data. Here we evaluate 7 neuroimaging workflow engines (Nipype, PSOM, SPM, FastR,
        LONI, Automatic Analysis and Pydpiper with 7 other scientific workflow
        engines (Taverna, Pegasus, Make, OpenMOLE, Nextflow, Galaxy and Toil) and
        3 popular Big Data frameworks (Hadoop MapReduce, Apache Spark and Dask) 
        against 4 different criteria: Workflow composition, Performance, Portability
        and Reproducibility. Scientific workflow engines are found to lack the 
        inherent qualities required to be successful scientific Big Data workflow 
        engines. However, Big Data frameworks are found exhibit features crucial
        to the processing of neuroimaging Big Data, although may lack some features
        necessary for the processing of neuroimaging data, such as data checkpointing and 
        standardized provenance tracking formats. Adaptations required to make Big
        Data frameworks compatible with the processing of neuroimaging Big Data 
        appear less significant than adaptation required to make current neuroimaging 
        workflows efficient in the processing of Big Data, thus making Big Data frameworks
        such as Dask and Spark good contenders for the processing of neuroimaging Big Data.
